Searching for long-period transiting planets in the \kepler\ light curves using supervised classification

### 2015-04-09 document/ms.tex
physical parameters plot and abstract edits

Many of the most dynamically important planets have orbits longer than
the baseline of existing transit surveys (\kepler, \KT).
Future surveys (\tess, \plato) will have such a short continuous coverage that
even habitable zone planets around M-dwarfs will only present a single transit
signal.
Searches for these transiting planets are plagued by false
signals---especially when pushed to low signal-to-noise---and statistical
studies of their population are complicated by weak constraints on the
physical parameters of the system and high rates of false positives.
We develop and present a computationally expensive but tractable method of
searching for single transits using supervised classification methods from
the machine learning literature.
For each month of photometry, we train a random forest classifier on a large
number of simulated signals injected into the photometry of the same star at
different times.
Then, the model's prediction as a function of transit time is evaluated and
times above a threshold probability---chosen for each star to yield a sample
with $\sim99$~percent purity---are given as candidate transits.
Each candidate must then pass a final round of vetting including BLAH BLAH
BLAH.
Applied to every light curve in the \kepler\ archive this method yields a
list of XXXX long-period transiting planet candidates.
Using an informative prior on their eccentricities, we derive weak constraints
on the orbital periods of the candidates and demonstrate that this puts an
upper limit of ZZZZ on the occurrence rate of these planets.

@@

In the 3500 light curves we searched for this \paper, we discovered one
convincing single transit signal at $830.80921\pm0.00015$~KBJD in the light
curve of the 14.9~Kep-mag G-dwarf KIC 10602068.
Despite the fact that this is a very large signal, its discovery has never
been reported.
Given the estimate of $\sim 60$ detectable single transits in the full
\kepler\ archival dataset, we expect about one discovery in 3500 light curves.

@@

The \citet{Huber:2014} parameters for this star place it as a G-dwarf with a
radius of $\sim 0.9\,R_\odot$ $2.02 \pm 0.25\,R_\mathrm{J}$.

@@

>>>>

Many of the most dynamically important planets have orbits longer than the
baseline of existing transit surveys (\kepler, \KT).
Future surveys (\tess, \plato) are planned to have shorter continuous coverage
that even habitable zone planets around M-dwarfs will only present a single
transit event.
Searches for these long-period transiting planets are plagued by false
signals---especially when pushed to low signal-to-noise---and statistical
studies of their population are complicated by weak constraints on the
physical parameters of the system and high rates of false positives.
We develop and present a computationally expensive but tractable method of
searching for single transits using supervised classification methods from
the machine learning literature.
For each star, we train several random forest classifiers on simulated signals
injected into different subsets of the data.
These models are evaluated on the raw photometry to assign a transit
probability at each time.
As a proof of concept, we apply this method to 3500 light curves from the
\kepler\ archival dataset and discover a previously unknown single transit
candidate.
Assuming a bound Keplerian orbit and using an informative prior on the
eccentricity, we measure a radius of $2\,R_\mathrm{J}$ and derive a weak
constraint on the orbital period.

@@

In the 3500 light curves we searched for this \paper, we discovered one
convincing single transit signal at $830.8093\pm0.0002$~KBJD in the light
curve of the 14.9~Kep-mag G-dwarf KIC 10602068.
Despite the fact that this is a very large signal, its discovery has never
been reported.
Given the estimate of $\sim 60$ detectable single transits in the full
\kepler\ archival dataset, we expect about one discovery in 3500 light curves.

@@

The \citet{Huber:2014} parameters for this star place it as a G-dwarf with a
radius of $\sim 0.9\,R_\odot$
$2.1 \pm 0.4\,R_\mathrm{J}$.

@@

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/corner.pdf}
\end{center}
\caption{%
Posterior constraints on the physical parameters of the body transiting KIC
10602068 assuming a bound Keplerian orbit.
\figlabel{corner}}
\end{figure}
